WDIAS : A Microservices-Based Weather Data Integration and Assimilation System\\

### 2020-05-31 method/sec_6-query.tex
Proofread Chapter 4

We used the query adapter primarily for supporting geo-spatial queries. As the primary service for searching for timeseries, it supports retrieval of timeseries metadata for external queries as well. The Appendix B described the search query capabilities within \acrshort{wdias}.

The system provides timeseries metadata query endpoints to search for existing timeseries metadata within the system using primary key attributes.
Also, it provides a set of geo-query endpoints, and users can perform geo-search queries with sending geo-information in geoJson format. The following geo-queries are supported by the system, and a detailed description appears in Appendix B.
\begin{itemize}
    \item Query locations within area
    \item Query parameters in locations
    \item Query timeseries by location
    \item Query timeseries by locations
    \item Query timeseries by Parameter
    \item Query timeseries in area
    \item Query timeseries in area by parameter
    \item Query all timeseries
\end{itemize}

>>>>

We used the query adapter primarily for supporting geo-spatial queries. As the primary service for searching for timeseries, it supports retrieval of timeseries metadata for external queries as well. Appendix B described the search query capabilities within \acrshort{wdias}.

The system provides timeseries metadata query endpoints to search for existing timeseries metadata within the system using primary key attributes.
Also, it provides a set of geo-query endpoints, and users can perform geo-search queries with sending geo-information in geoJson format. The following geo-queries are supported by the system, and a detailed description is presented in Appendix B.
\begin{itemize}
    \item Query locations within area
    \item Query parameters in locations
    \item Query timeseries by location
    \item Query timeseries by locations
    \item Query timeseries by Parameter
    \item Query timeseries in area
    \item Query timeseries in area by parameter
    \item Query all timeseries
\end{itemize}

### 2020-05-31 results/sec_1-test_plan.tex
Work load done
Proofread Chapter 4

The test plan is to perform load testing on the whole system and analyze the scalability of the system while measuring the operations performed on each module. Two variables can vary while doing performance testing.
\begin{enumerate}
    \item Number of requests made to the system at a given time called as \acrfull{rps}
    \item Request size
\end{enumerate}

A timeseries is a series of data points in time order. The system may receive the data points of a timeseries in multiple requests. The request size can vary based on the use case from one data point to multiple data points. For example;
\begin{itemize}
    \item A weather station may send the current water level in a regular 1 minute intervals. In such a case, it always comes as a request with one data point with a higher frequency.
    \item Due to resource issues such as batteries, a weather station can collect data points for a given period and send as a batch. An example scenario would be, a weather station can collect the precipitation at each 5 minute period and send all the data after collecting for one hour.
    \item The forecast precipitation data from the \acrshort{wrf} model extract for a few days in hourly intervals and store them.
\end{itemize}

The percentage of number of requests per each data type that comes to the system at a given time can be varied depending on the situation. The Majority of weather data requests come from weather stations and other observation tools. Then we need to validate and modify those timeseries data and store them as new timeseries that can directly feed into the NWMs. These weather stations can send the weather data at different frequencies with different parameters such as precipitation, temperature, humidity, and wind direction. Most of the timeseries mentioned above are scalar timeseries. When compared to scalar data, parameters such as wind direction are vector timeseries with a lesser percentage of requests. On the other hand, most of the grid type data was generated as results of NWMs. But those grid data produce in less frequency due to the cost of the computer resource to produce results. After considering those factors we came up with 70\% scalar, 20\% vector, and 10\% grid percentage values as the expected requests rate ratios.
As an upper limit of such scenarios while designing the performance testing, it uses the following;
\begin{itemize}
    \item Hourly (24 data points)
    \item Every 30 minutes (48 data points)
    \item Every 15 minutes (96 data points) - One request is equivalent to a set of data points sent by a weather station in 15 minutes interval for a single day
\end{itemize}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{List of Test Plans}
\label{subse:test_plan_flow}
Following are the test cases which are planned to performance test cases;
\begin{enumerate}
    \item Test Setup to create timeseries in 1hr, 30min and 15min intervals, create metadata of the timeseries and create random extension triggers
    % \item Extensions
    % \begin{itemize}
    %     \item Create Extensions for /Aggregation\_Accumulative, /Interpolation Linear, /Validation Missing Values (OnChange and OnTime)
    %     \item Plan for the 15 minutes of test run with the request size of 15min data. (total 0.25 hours)
    %     \item Do with Import Timeseries with error data which will go through extensions.
    % \end{itemize}
    \item Import + Extension + Export + Timeseries Queries
    \begin{itemize}
        \item Plan for 30 minutes of the test run with the request size of 1hr (60min) data
        \item Plan for 30 minutes of the test run with the request size of 30min data
        \item Plan for 30 minutes of the test run with the request size of 15min data
        \item Plan for 30 minutes of the test run with the request size of 15min data with auto-scaling
        % \item Test plan run against 60min, 30min and 15min request size of data. Another test plan runs with enabling the auto-scaling
    \end{itemize}
    \item Query
    \begin{itemize}
        \item Query Timeseries
        \item Plan for the 5 minutes of test run
    \end{itemize}
\end{enumerate}

>>>>

The test plan is to perform load testing on the whole system and analyze the scalability of the system while measuring the operations performed on each module. Two variables can vary while doing performance testing.
\begin{enumerate}
    \item Number of requests made to the system at a given time i.e., \acrfull{rps}
    \item Request size
\end{enumerate}

A timeseries is a series of data points in time order. The system may receive the data points of a timeseries in multiple requests. The request size can vary based on the use case from one data point to multiple data points. For example;
\begin{itemize}
    \item A weather station may send the current water level in a regular 1 minute intervals. In such a case, it always comes as a request with one data point with a higher frequency.
    \item Due to resource issues such as batteries, a weather station can collect data points for a given period and send as a batch. An example scenario would be, a weather station can collect the precipitation and send all the data as a batch.
    \item The forecast precipitation data from the \acrshort{wrf} model extract for a few days in hourly intervals and store them.
\end{itemize}

The percentage of number of requests per each data type that comes to the system at a given time can be varied depending on the situation. The Majority of weather data requests come from weather stations and other observation tools. Then we need to validate and modify those timeseries data and store them as new timeseries that can directly feed into the NWMs. These weather stations can send the weather data at different frequencies with different parameters such as precipitation, temperature, humidity, and wind direction. Most of the timeseries mentioned above are scalar timeseries. When compared to scalar data, parameters such as wind direction are vector timeseries with a lesser percentage of requests. Alternatively, most of the grid type data was generated as results of NWMs. But those grid data produce in less frequency due to the cost of the computer resource to produce results. After considering those factors we came up with 70\% scalar, 20\% vector, and 10\% grid percentage values as the expected requests rate ratios.
As an upper limit of such scenarios while designing the performance testing, it uses the following;
\begin{itemize}
    \item Hourly (24 data points)
    \item Every 30 minutes (48 data points)
    \item Every 15 minutes (96 data points) - One request is equivalent to a set of data points sent by a weather station in 15-minute interval for a single day
\end{itemize}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{List of Test Plans}
\label{subse:test_plan_flow}
Following are the test cases which are planned to performance test cases;
\begin{enumerate}
    \item Test setup to create timeseries in 1-hour, 30-minute and 15-minute intervals, create metadata of the timeseries and create random extension triggers
    % \item Extensions
    % \begin{itemize}
    %     \item Create Extensions for /Aggregation\_Accumulative, /Interpolation Linear, /Validation Missing Values (OnChange and OnTime)
    %     \item Plan for the 15 minutes of test run with the request size of 15min data. (total 0.25 hours)
    %     \item Do with Import Timeseries with error data which will go through extensions.
    % \end{itemize}
    \item Import + Extension + Export + Timeseries queries
    \begin{itemize}
        \item Plan for 30 minutes of the test run with the request size of 1-hour (60-minute) data
        \item Plan for 30 minutes of the test run with the request size of 30-minute data
        \item Plan for 30 minutes of the test run with the request size of 15-minute data
        \item Plan for 30 minutes of the test run with the request size of 15-minute data with auto-scaling
        % \item Test plan run against 60min, 30min and 15min request size of data. Another test plan runs with enabling the auto-scaling
    \end{itemize}
    \item Query
    \begin{itemize}
        \item Query timeseries
        \item Plan for the 5 minutes of test run
    \end{itemize}
\end{enumerate}

### 2020-05-31 results/sec_2-workload.tex
Proofread Chapter 4

As explained in the research methodology (\cref{ch:method}), we selected six primary attributes from the timeseries metadata while implementing the system architecture. Before storing the data in \acrshort{wdias}, we need to register timeseries metadata for the timeseries, and are required to provide values for the six attributes. During the test for location attribute, we selected set of locations all over the world as a generic case to include all the locations without binding to a specific area.

@@

We used the Apache JMeter for performing the load test since it is a widely using open source tool which supports distributed load testing. As mentioned in the JMeter Best Practices, "If your test needs large amounts of data - particularly if it needs to be \emph{randomized}, create the test data in a file that can be read with CSV Data set. This avoids wasting resources at run-time". While running the load test, JMeter iterates over the timeseries metadata CSV file and assigns a new thread to work on the test scenario with given timeseries metadata. Instead of providing the randomness at run time, we stored the timeseries metadata in random order that satisfies the percentage of 70\% scalar, 20\% vector, and 10\% grid, as mentioned in \cref{se:test_plan}.
Before running the test cases, we generated the timeseries metadata in random order and wrote them into a CSV file during the setup phase. The metadata CSV file arranges in a way that, within every ten lines, seven lines are scalar timeseries, two lines are vector timeseries, and 1 line is a grid timeseries.

@@

While preparing the data, we created three sets of timeseries based on the time interval, such as hourly (60min), 30min, and 15min data, with modifying the replicated data. The above method reduced the overhead of filtering data during performance testing. We also set up the JMeter as a containerized application, which allows us to run inside the k8s cluster. As an optimization for the JMeter container creation, we avoid adding extensive test timeseries data, which causes the container size to be large and making the build process slower. Rather than doing that, we used extract scripts while running the container and extract the data into the container. For each test plan, we used a date counter and increment the date after one full cycle of timeseries metadata CSV file is processed. When the date counter increases, it reads the real data for that day. After the date counter advances to the next month, we repeat reading data from the beginning of the month. To provide more randomness, we switch over five locations during the date increment. The JMeter reads the data via the JSR223 scripts, and we have written those scripts in a generalized style such that it is possible to tweak and use if there are more location data available.

@@

\cref{fi:test_prod_throughtput_shaping_timer} shows the throughput shaping timer configurations that we used for the load testing, and it is similar to the load test plan described in \cref{se:test_plan}. The maximum peak load that can be had during the load test is 300 \acrshort{rps} (equivalent to 18,000 requests per minute). The following list shows all the test plans that we used during the performance testing:

@@

\begin{lstlisting}[language=sh, caption=Performance Test Help]
-h | --help: Usage
  test-dev enable <MODULE>
    - MODULE: import(i) | export(e) | extension(x) | all(a)

@@

Users can use one of the above methods to schedule microservice on physical nodes for better performance. For the moment, we used node affinity to schedule the microservices. We chose the above method since it allows us to schedule all the microservices in a node when there is only a single physical node available. Microservices are assigned to each node in \cref{tab:aws_eks_nodes} based on the node label as below;
\begin{itemize}
    \item \emph{core} -- metadata, extensions, query, status and extension services
    \item \emph{grid} -- grid adapter, import and export grid data
    \item \emph{scalar} -- scalar and vector adapters, import and export of same data types
    \item \emph{test} --  JMeter and metric server
\end{itemize}
\cref{fi:eks_node_setup} shows the overview of the microservices assignment to each node in the \acrshort{eks} setup. Further, it shows the connectivity of the nodes and the data interactions via the arrows. We scheduled the microservices in the core labeled node together, since most of those services are communicating together, and running them inside one physical node reduces the latency. Then we separate scalar and vector microservices and their databases to separate the load from the core node while storing scalar and vector timeseries data. As same as, we assigned microservices to grid and test nodes based on the higher bandwidth requirements.

>>>>

As explained in the research methodology (in \cref{subse:timeseries_key_attributes}), we selected six primary attributes from the timeseries metadata while implementing the system architecture. Before storing the data in \acrshort{wdias}, we need to register timeseries metadata for the timeseries, and are required to provide values for the six attributes. During the test for location attribute, we selected set of locations all over the world as a generic case to include all the locations without binding to a specific area.

@@

We used the Apache JMeter 5.0 version \cite{ApacheSoftwareFoundationApacheJMeter} for performing the load test since it is a widely using open source tool which supports distributed load testing. As mentioned in the JMeter best practices, "If your test needs large amounts of data - particularly if it needs to be \emph{randomized}, create the test data in a file that can be read with CSV data set. This avoids wasting resources at run-time". While running the load test, JMeter iterates over the timeseries metadata CSV file and assigns a new thread to work on the test scenario with given timeseries metadata. Instead of providing the randomness at run time, we stored the timeseries metadata in random order that satisfies the percentage of 70\% scalar, 20\% vector, and 10\% grid, as mentioned in \cref{se:test_plan}.
Before running the test cases, we generated the timeseries metadata in random order and wrote them into a CSV file during the setup phase. The metadata CSV file arranges in a way that, within every ten lines, seven lines are scalar timeseries, two lines are vector timeseries, and 1 line is a grid timeseries.

@@

While preparing the data, we created three sets of timeseries based on the time interval, such as hourly (60-minute), 30-minute, and 15-minute data, with modifying the replicated data. The above method reduced the overhead of filtering data during performance testing. We also set up the JMeter as a containerized application, which allows us to run inside the k8s cluster. As an optimization for the JMeter container creation, we avoid adding extensive test timeseries data, which causes the container size to be large and making the build process slower. Rather than doing that, we used extract scripts while running the container and extract the data into the container. For each test plan, we used a date counter and increment the date after one full cycle of timeseries metadata CSV file is processed. When the date counter increases, it reads the real data for that day. After the date counter advances to the next month, we repeat reading data from the beginning of the month. To provide more randomness, we switch over five locations during the date increment. The JMeter reads the data via the JSR223 scripts, and we have written those scripts in a generalized style such that it is possible to tweak and use if there are more location data available.

@@

\cref{fi:test_prod_throughtput_shaping_timer} shows the throughput shaping timer configurations that we used for the load testing, and it is similar to the load test plan described in \cref{se:test_plan}. The maximum peak load that can be had during the load test is 300 \acrshort{rps} (equivalent to 18,000 requests per minute). The following the test plans that we used during the performance testing:

@@

\begin{lstlisting}[language=sh, caption=Automated performance test plans.]
-h | --help: Usage
  test-dev enable <MODULE>
    - MODULE: import(i) | export(e) | extension(x) | all(a)

@@

Users can use one of the above methods to schedule microservice on physical nodes for better performance. For the moment, we used node affinity to schedule the microservices. We chose the above method since it allows us to schedule all the microservices in a node when there is only a single physical node available. Microservices are assigned to each node in \cref{tab:aws_eks_nodes} based on the node label as below;
\begin{itemize}
    \item \emph{core} -- metadata, extensions, query, status and extension services
    \item \emph{grid} -- grid adapter, import and export grid data
    \item \emph{scalar} -- scalar and vector adapters, import and export of same data types
    \item \emph{test} --  JMeter and metric server
\end{itemize}
\cref{fi:eks_node_setup} shows the overview of the microservices assignment to each node in the \acrshort{eks} setup. Further, it shows the connectivity of the nodes and the data interactions via the arrows. We scheduled the microservices in the core labeled node together, since most of those services are communicating together, and running them inside one physical node reduces the latency. Then we separate scalar and vector microservices and their databases to separate the load from the core node while storing scalar and vector timeseries data. Similarly, we assigned microservices to grid and test nodes based on the higher bandwidth requirements.
